Postural developments mediate children's visual access to social information

### 2018-01-24 writeup-cogsci/cogsci2018_faceOnly.Rmd
intro edits

Children are deeply engaged in learning from others around them  [@csibra2009natural; @meltzoff2007like] and attend to the social information in their environment from their earliest days. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and follow overt gaze shifts by 6 months of age [@gredeback2008microstructure, @gredeback2010development]. And when infants free-view videos,infants tend to look mostly at faces at the expense of all of the other complex natural scenes -- though older infants also start to look more towards people's hands and the actions they are performing [@frank2012measuring; @frank2014visual].

>>>>

Children are deeply engaged in learning from others around them  [@csibra2009natural; @meltzoff2007like] and attend to the social information in their environment from their earliest days. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and follow overt gaze shifts by 6 months of age [@gredeback2008microstructure, @gredeback2010development]. And when infants free-view videos,they tend to look mostly at faces at the expense of all of complex information--though older infants also start to looktowards people's hands and the actions they are performing [@frank2012measuring; @frank2014visual].
